|

### 2021-08-10 03-Chp-Systematic-Review.Rmd
End of day:

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---
```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```

@@

<!-- -   TODO Examine how many times a primary study was included in a review -->
<!-- -   TODO Look at whether searching preprints made any difference to my results -->
<!-- -  TODO Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project) -->

<!-- TODO Extra studies to include: -->

<!-- * Smeet et al. reference in the CPRD analysis -->
<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
<!-- * Statins and the risk of dementia Jick -->

@@

The importance of

I found that

@@

The aim of this chapter is to systematically review all available literature on the association between blood levels of total cholesterol and it's constituent parts (HDL-c,LDL-c and triglycerides) on the subsequent risk of dementia.

Based on the review of existing literature, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.

Only by looking across all available evidence can the true, given the often limited use of one type of evidence (RCTs are hard to do, obs studies are biased).

Literature con

Systematic reviews aim to transparently and reproducibly identift

<!-- TODO Need to seriously improve this -->

@@

This systematic review was performed in conjunction with a team of secondary reviewer, These included Alexandra MacAleenan, Athena Sheppard, Matthew Lee and Lena Schmidt.

@@

### Search strategy and and study selection

I systematically search electronic bibliographic databases to identify potentially relevant records. The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist. The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed. An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full draft search strategies for each database are presented in Appendix \@ref(appendix-search-strategy). <!-- TODO Need to actually attach each search strategy. Should be able to loop through search strategy results. -->

@@

To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 14" in Table \@ref(tab:searchOverview-table)) was screened. If any potentially relevant studies are identified, their titles and abstracts were searched for key terms that can be incorporated into the filters to improve search sensitivity.

@@

The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University). I also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials. As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).

The abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand. <!-- TODO how were these searched? Date and other range -->

Grey literature was also searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. I also searched bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies. Finally, the reference lists of included studies were searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

@@

<!-- Include table with overview of search strategy here: summarise topics and how they were combined -->

#### Study selection

@@

Screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.

Full-text screening will also be completed in full by the primary author. A second reviewer screened a random sample (approx 10%) of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage were recorded. Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague. A PRIMSA flow diagram will be produced to document how records moved through the review.[@page2021]

@@

We will seek studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI. Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.

Participants were free (or assumed to be free) of dementia/MCI at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression. No limits will be placed on the sample size of included studies.

Eligible studies defined dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. <!-- TODO do i actually want to include MCI? -->
 For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g. an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g. no dementia or dementia/MCI/dementia) based on this definition.

No limitations will be imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.

@@

Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded. Studies which present no evidence of attempting to exclude prevalent cases from their analyses will also be excluded. Studies that measure change in continuous cognitive measures (e.g. MoCA score) without attempt to map these scores to ordinal groups (e.g. no dementia/MCI/dementia) will be excluded. Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study's status. Studies that are reported in insufficient detail (e.g. only in conference abstracts, new, letters, editorials and opinion) will be excluded. Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles. Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where the lipid-regulating agent is included in each arms (e.g. for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) will be excluded.

Excluded studies performing autopsy unless it was done under accepted criteria Exclude studies using a dietary intervention, for example omega-3 fatty acid enriched diet, as it hard to disentangle the effect of other elements contained within te diet, vs simple tablet based supplements of

<!-- TODO Expand on rationale for exclusion of cross-sectional studies. Dementia is a disease severly at risk of differential recall, leading to misclassification bias. By using prospective studies, the potential for this bias is reduced. -->

@@

#### Assessment of inter-rater reliability

Inter- and intra-rater reliability was assessed for a 10% sub-sample of records at the title and abstract screening stage. Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.

If this approach demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does. [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review, this is an important characteristic.

@@

@@

Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorizing lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.

Following guidance for a dose response meta-analysis, I picked midpoint for all studies where bands were provided (extremely common in the case of lipids)

This analysis was unusual, as multiple methods of integration and analysis were required with data spanning many forms.

A piloted data extraction for was used. I extracted the data in the first instance and subset was checked by a colleague for accuracy.

<!-- TODO Cross reference with the data extraction issues here - i.e. not providing qratile cut-off values, not poviding numbers per group, etc. -->

Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:

@@

#### Studification

Multiple publications resulting from the analysis of the same data were included and grouped ().

In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.

@@

This was particular important for the dose response meta-analysis, we

Use the example of getting the cut-off points from the

@@

Not interchangeable in the context of systematic review. If outcome is rare, odds and risk ratios approximate each other, but the hazard ratio is measuring something completely different, by taking into account time-to-event in each treatment group.

Several existing reviews do not distinguish between the two types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.

The likely effect of this is that the overall effect measures are biased towards . . . . ?

Can you predict the direction of effect from a

Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis

@@

Some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but not documented in review text.

While the analysis of change scores is feasible, as they were explicityl

@@

A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(intro-triangulation) and Section \@ref(triangulation-overview) for an overview of triangulation). To enable this triangulation exercise, a detailed and structured risk of bias assessment formed an important part of this review.

@@

This move was prompted by a unclear definition of "methodological quality" which could include facets such as, and challenges in the comparison of results from different tools.

As part of this, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.

@@

In this review, domain-based tools were used to assess the risk of bias for each result in each included study. The study design-specific tools are introduced and discussed in more detail in the following sections.

In addition, the tool also aim to capture the potential direction of bias for each given domain. An optional question at the end of each domain, e.g. for Domain 1 of the RoB2 tool: "What is the predicted direction of bias arising from the randomization process?", possible responses included

* Not applicable 
* Favours experimental 
* Favours comparator
* Towards null 
* Away from null 
* Unpredictable

@@

Risk of bias assessment in randomised controlled trials was performed using the domain-based risk-of-bias assessment tool appropriate to the study design. Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019], 
The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result. Acceptable judgements include: low risk of bias, some concerns, high risk of bias. Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool.

One a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to

@@

For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk of bias in non-randomised studies - of interventions) <!-- TODO Capitalise appropriately --> tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result. Similar to the RoB 2, it has a number of prompting questions per domain, with judgements including. Ideally, obs studies assessed in reference to an idealised randomised controlled trial. Further, the rare overall judgement of Low should be considered equivalent to a randomised controlled trial.

For non-randomised studies of exposures (NRSE), I opted to use a preliminary version of the ROBINS-E tool, despite it still being in development.[@morganr2020] While the signalling questions for each domain are yet to be confirmed, the overarching domains have been finalised.

Despite these limitations, I chose this approach in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] The motivation for this decision was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS. In addition, using a domain-based tool enabled better comparison with risk-of-bias assessments performed for the other study designs.

@@

<!-- TODO This next bit is not all true -->

At present, no risk-of-bias assessment tool for Mendelian randomization studies is available. Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies. A copy of this tool is available in Appendix \@ref(appendix-mr-rob). Advance results from this review of bias assessment in MR studies were obtained from contact with the authors.

@@

A recent shift towards the assessment of missing evidence due to selective non-reporting (as distinct from the selective reporting of a single result from multiple planned - handled in Domain 5 of the RoB 2 tool for example).

As part of this review, I piloted the RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool. <!-- TODO CITATION NEEDED --> Results were visualised

This additional appraisal marks a departure from the protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence. This is because the tool did not exist when the protocol was originally registered.

@@

Studies were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies).

@@

Meta-analysis is an important method of . . .

Both a fixed-effect and random-effects meta-analysis model was.

For

Need formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.

This analytical approach was used for

$u$

@@

where ...

@@

This analytical approach was used for cases where the exposure was dichotomous (e.g. statin use or not, hypercholesterolemia or not).

@@

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results? -->
 while this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.

Where possible, data for all exposure groups was extracted, and this <!-- TODO ??? -->
. Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g. if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L).

<!-- Taken from another paper: "A potential non-linear association was evaluated using a restricted cubic spline model with three knots at the 10th, 50th and 90th percentile of frequency of the exposure [@orsini2012meta]" -->

<!-- TODO Do I initially want to fit a linear relationship across categories and  -->
A XXXX spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of an exposure can have an effect versus the "normal" reference dose. Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table). Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.

@@

When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the widht of the higest category was the same as the one immediately below it. Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).

I assumed the width of the category to be the same as the adjacent category.
When the lowest category was open ended, I set the lower boundary to zero.

@@

### Patient and public involvement

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---
```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```

@@

<!-- -   TODO Look at whether searching preprints made any difference to my results -->

<!-- TODO Extra studies to include: -->
<!-- * Smeet et al. reference in the CPRD analysis -->
<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
<!-- * Statins and the risk of dementia Jick -->

@@

Systematic reviews are a type of research that aim to use all existing evidence to provide the best answer to an important research question. They do this by finding and combining the results from many related primary research studies. Reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; assessment of each study's methods.

This chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides), and treatments that change these levels, and dementia.

There were 127 primary studies <!-- TODO check this -->that contained information on this relationship. I found that statins reduce the risk of Alzheimer's disease, but had no effect of vascular dementia. Lipids were not associated with any outcome. The methods used in some of the primary studies meant that I was less confident in the accuracy of their results.

The use of the results of this review in subsequent chapters is dicussed.

@@

In this chapter, I describe a comprehensive systematic review of the relationship between blood lipid levels, and treatments that modify them, and the subsequent risk of dementia and related outcomes. This analysis sought to address two specific aims.

Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist. These include randomised controlled trials, observational studies of different analytical design (cohort, case-control, etc), and Mendelian randomisation studies. However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types. Collating these diverse evidence sources is important, as if the observed association between lipids and dementia is constant across them, it increases our confidence in the association. As such, the primary aim of this analysis was to systematically review all available literature, regardless of study design.

Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence syntheists but may contain important unpublished studies. As an adjunct analysis to the systematic review presented in this chapter, I sought to quantify the additional evidential value of including preprints. This inclusion of preprint serves makes use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).

@@

In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes. Due to the scale of the project, this systematic review was performed in conjunction with a team of secondary reviewer. These included Alexandra MacAleenan, Athena Sheppard, Matthew Lee and Lena Schmidt. In addition, Sarah Dawson, and information specialist, provided input to the design of the search strategy.

@@

### Search strategy

I systematically search electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records"). The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist. The strategy included terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed. An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy). <!-- TODO Need to actually attach each search strategy. Should be able to loop through search strategy results. -->

@@

When searching the bibliographic databases, study design filters were employed to try and reduce the screening load. To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.

@@

The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection. As the contents of the Web of Science Core Collection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases). I also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.

In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies.

Grey literature was also searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. In addition, the abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand. <!-- TODO how were these searched? Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"<!-- TODO CITATION NEEDED -->).

@@

### Study selection

@@

Following deduplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.

Similarly, I completed all full-text screening, with a random ~10% being screened in duplicate by a second reviewer. In addition, any records identified I identified as being difficult to assess against the inclusion criteria were screened in duplicate. Reasons for exclusion at this stage were recorded. Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague. A PRIMSA flow diagram was produced to document how records moved through the review.[@page2021]

The criteria used to assess eligibility are presented in the subsequent sections.

@@

I sought to include studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI. <!-- TODO Do I actually want to include MCI? --> Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.

Participants were free (or assumed to be free) of dementia/MCI <!-- TODO Do I actually want to include MCI? -->  at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression. No limits were placed on the sample size of included studies.

Eligible studies defined dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. <!-- TODO CITATION NEEDED --> <!-- TODO do i actually want to include MCI? --> For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g. an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g. no dementia or dementia/MCI/dementia) based on this definition.

No limitations were imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.

@@

Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews were excluded. Studies which present no evidence of attempting to exclude prevalent cases from their analyses were also excluded. Studies that measure change in continuous cognitive measures (e.g. MoCA score) without attempt to map these scores to ordinal groups (e.g. no dementia/MCI/dementia) were excluded. Conference abstracts with no corresponding full-text publication were examined, and I contacted authors to obtain information on the study's status. Studies that are reported in insufficient detail (e.g. only in conference abstracts, new, letters, editorials and opinion) were excluded. Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles. 
<!-- TODO Expand on rationale for exclusion of cross-sectional studies. Dementia is a disease severly at risk of differential recall, leading to misclassification bias. By using prospective studies, the potential for this bias is reduced. -->

Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where the lipid-regulating agent is included in each arms (e.g. for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) were excluded. Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet. Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.

@@

### Validation of screening process

Inter- and intra-rater reliability during the screening stage were assessed for a 10% sub-sample of records at the title and abstract screening stage. Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e. assessment of conistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e. assessment of accuracy).

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does. [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is an important characteristic.

@@

If this assessment demonstrated issues with the screening process, a larger proportion of records would have been dual-screened.

@@

Data extraction was performed using a piloted data extraction form. Extracted items included: article metadata (year of publication, author list, journal), study characteristics (location, cohort name, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value). All data was extracted the data in the first instance and was checked for accuracy by a second member of the review team.

#### Harmonisation of cholesterol measures

Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorizing lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable. <!-- TODO This might not be as accurate now given the focus on dose response --> <!-- TODO Cross reference with the data extraction issues here - i.e. not providing qratile cut-off values, not poviding numbers per group, etc. --> Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:

@@

#### Study-fication

As part of the data extraction process, multiple resords resulting from the analysis of the same data were included and grouped into single units, hereafter called studies. This is likely in the advent of multiple papers reporting results on the same cohort, but say, at different time points. Study-fication builds out the most comprehensive accounts of the studies and results from as many published articles were applicable.

@@

This was particularly important for the dose response meta-analysis, where the number of participants and the cut-offs per category were often not reported.

<!-- TODO Use the example of getting the cut-off points from the  -->

@@

The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review. If the outcome is rare, odds and risk ratios approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account time-to-event in each treatment group.

Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect. In adddition, there is some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but this is not accurately documented in the review text.

<!-- TODO Need to really fix this -->

<!-- The likely effect of this is that the overall effect measures are biased towards . . . . ? -->

<!-- Can you predict the direction of effect from a  -->

<!-- Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis  -->

@@

@@

A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Section \@ref(intro-triangulation) for the results of this qualitative analysis). To enable this triangulation exercise, a detailed and structured risk of bias assessment formed an important part of this review.

@@

This move was prompted by a unclear definition of "methodological quality" which could include facets such as, and challenges in the comparison of results from different tools. As part of this, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.

@@

In this review, domain-based tools were used to assess the risk of bias for each result in each included study. The study design-specific tools are introduced and discussed in more detail in the following sections. In addition, the tool also aim to capture the potential direction of bias for each result. Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable".

@@

Risk of bias assessment in randomised controlled trials was performed using the domain-based risk-of-bias assessment tool appropriate to the study design. Randomized controlled trials were assessed using the RoB2 tool.[@sterne2019]

The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result. Acceptable judgements include: low risk of bias, some concerns, high risk of bias. Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool. Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.

@@

For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result. Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “Low risk”, “Moderate risk”, “Serious risk” and “Critical risk”. Ideally, observationals studies should be assessed in reference to an idealised randomised controlled trial. Further, the rare overall judgement of "Low" is considered equivalent to a randomised controlled trial.

For non-randomised studies of exposures (NRSE), I opted to use a preliminary version of the ROBINS-E tool.[@morganr2020] The tool is still in development, but while the signalling questions for each domain are yet to be confirmed, the overarching risk-of-bias domains have been finalised. The motivation for this using this tool above other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS. <!-- TODO CITATION NEEDED --> In addition, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs.

@@

At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available. Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies (advance results from this review were obtained from contact with the authors.). <!-- TODO CITATION NEEDED --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob).

@@

A recent shift towards the assessment of missing evidence due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - is demonstrated via the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool. <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers. <!-- TODO CITATION NEEDED -->

This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence. This is because the tool did not exist when the protocol was originally registered.

@@

An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies across

Where individual studies were deemed comparable, they were incoroporated into a quantitative analysis or "meta-analysis". <!-- TODO CITATION NEEDED --> Meta-analysis provides a summary or pooled effect estimate across studies.

Of note, studies were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies). The results from each individual analytical approach were summarised, but are compare and contrasted more fully in the triangulation exercise presented in Chapter \@ref(discussion-heading)

@@

<!-- Where both the outcome and the exposure were dichotmous, or the -->

Both a fixed-effect and random-effects meta-analysis model was employed to combine the different included studies. <!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses. --> The fixed-effect method was implemented as:

@@

<!-- where ... -->

@@

@@

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results? --> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.

Where possible, data for all exposure groups was extracted. <!-- TODO ??? --> Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g. if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L).

<!-- Taken from another paper: "A potential non-linear association was evaluated using a restricted cubic spline model with three knots at the 10th, 50th and 90th percentile of frequency of the exposure [@orsini2012meta]" -->
<!-- TODO Do I initially want to fit a linear relationship across categories and  -->
A <!-- TODO confirm type of spline --> spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of an exposure can have an effect versus the "normal" reference dose. Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table). Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.

@@

When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the width of the higest category was the same as the one immediately below it. Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).

@@

<!-- TODO PRISMA must include reasons for exclusion - extract from  -->
